### 2020-12-25 latex/introduction.tex
More edits to VNHC and intro to clarify the differences between us and Alireza

Each of these research areas use different formulations of virtual
nonholonomic constraints.
Furthermore, the most recent literature surrounding virtual nonholonomic constraints
has focused on enforcing stable periodic orbits for hybrid mechanical systems
with impacts.
To the best of our knowledge, no one has attempted to create a single unified
framework of virtual nonholonomic constraints for general mechanical systems.
Moreover, no one has studied how virtual nonholonomic constraints can be used for energy
injection, where periodic motion is not desirable.
This thesis attempts to fill these gaps in the research.

>>>>

The most recent literature surrounding virtual nonholonomic constraints
has focused on enforcing stable periodic orbits for hybrid mechanical systems
with impacts.
To the best of our knowledge, no one has studied how virtual nonholonomic
constraints can be used for energy injection, where periodic motion is not
desirable.
This thesis attempts to fill this gap in the research.
For more detail on the differences between this thesis and the existing research
on virtual nonholonomic constraints, see Chapter \ref{ch:vnhc-compare}.

### 2020-12-25 latex/vnhcs.tex
More edits to VNHC and intro to clarify the differences between us and Alireza

>>>>

\section{Comparison with Existing VNHC Literature}\label{ch:vnhc-compare}

Griffin and Grizzle were the first to use the unactuated conjugate of momentum
to define relative degree \(\{2,\ldots,2\}\) VNHCs in
\cite{nhvc_dynamic_walking} and \cite{nhvc_gait_optimization}.
\citet{hybrid_zero_dynamics_bipedal_nhvcs} used this idea to define
the unactuated coordinate \(q_u = B^\perp q\), derive the unactuated momentum in
Lagrangian coordinates, and specify that a VNHC must use this unactauted
momentum.
These ideas are what inspired us to develop the theory of simply actuated
Hamiltonian systems, which is more suited to this area of research than
Lagrangian mechanics. 
Furthermore, our definition of a VNHC is more general than that of Griffin and
Grizzle.
They defined a VNHC as a relation \(h(q,\sigma_u)\) (where \(\sigma_u\) is the
Lagrangian mechanics proxy for \(p_u\)), while our definition of VNHCs allows
for relations that use the full phase.
Moreover, we are the first to provide the definition of regular VNHCs, and to
provide the characterization in Theorem \ref{thm:vnhc-regularity}.

\citet{hybrid_zero_dynamics_bipedal_nhvcs} were the first to derive the
constrained dynamics for VNHCs of the form \(h(q,\sigma_u)\).
In our derivation of the constrained dynamics, we use the same assumptions as
they do, with the additional assumption that one can solve for 
\(q_a = f(q_u,p_u)\) on \(\Gamma\).
While this means the constrained dynamics in
\cite{hybrid_zero_dynamics_bipedal_nhvcs} hold for a larger class of VNHCs, 
their derivations are terse and unclear.
By making this additional assumption, we were able to find a the constrained
dynamics in simply actuated coordinates, which are much more physically
intuitive.
Having the constrained dynamics in simply actuated coordinates will also
allow us to more easily study energy injection properties of VNHCs in the next
two chapters.
